\chapter{Modelization of Bloc Rigid of instrument}


%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{Introduction}

In this chapter we describe how rigid bloc of instrument are handled in \PPP. In this approach
we try to have a unified description of all type of instrument that can be embeded
together in a rigid block. The type of instrument under consideration are :

\begin{itemize}
   \item   camera ;
   \item   clinometers ;
   \item   targets ;
   \item   GNSS ;
   \item   IMU;
   \item   others ?
\end{itemize}

At the time being, the implementation if far from complete and we have 
the following restriction :

\begin{itemize}
   \item   only camera and clinometers are handleds
   \item   a block must contain at least one camera  (btw, what would be the interest of a clinometers only block);
   \item   the system can handle a single block (not a hard constraint, just need to give access to mutiple block, an to have data
           to check the implementation...)
\end{itemize}



%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{Formalisation}

%-----------------------------------------------------
\subsection{Repair of the block}

For each bloc $k$ we have an unknown pose  $\mathcal{P}_k=(R_k,C_k)$
that compute the transformation between bloc-coordinate $p^B_k$
and word coordinates $P_w$:

\begin{equation}
    p_w =  \mathcal{P}_k(p^B_k) =  C_k + R_k   p^B_k
\end{equation}

In the following, we will consider instrument belonging to the
same block and we will omit the index $k$ because
block are independant.

%-----------------------------------------------------
\subsection{Equation between cameras}

Let  :

\begin{itemize}
    \item $B_j$ and $B_j$ be pose of two cameras of the same block,
    \item $t$ , $t'$ be two time stamps;
    \item $P_{i,t}$ and $P_{j,t}$  the poses of camera
	    $i$ and $j$ at time stamp $t$.
\end{itemize}

If the bloc is rigid, the transformation between $B_i$ and $B_j$ 
is the same than between $P_{i,t}$ and $P_{j,t}$. We have :

\begin{equation}
    B_j (p^B) =  p_j  \; ; \;
\end{equation}


\subsection{Targets}

Targets can be a block of rigid target  alone , for example
if we have one (or several) pannel of target as used in CERN data-set, and simultaneously 
some target in word coordinates, we can no longer  consider that the panel is "the" system
of coordinates and we have to introduce multiple coordinate system.

Another case of use, is when we "stick" targets on a camera (the so called 
"arroseur arros\'e" or "bitter bit").
\COM
{
}

%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{User's point of view : introduction}


From the user point's of view, there is $3$ kind of command :

\begin{itemize}
    \item  command for creating/editing  the block, we add instrument and posible
	    constraint between them; this the command {\tt BlockInstrEdit};

    \item  command for initializing the position/orientation  of instrument  inside the bloc,
            command {\tt BlockInstrInitCam} and {\tt   BlockInstrInitClino};

    \item  command for using the  bloc in adjsutment with other measures;
           this is done with parametrization of {\tt OriBundleAdj}.

    \item  make a report on a bloc with {\tt ReportBlock}.
\end{itemize}

The formalism allow to have several bloc in the same adjustement, also this aspect has not been tested
for now (and consquently is probably not working completely).
The blocs are saved in the folder {\tt MMVII-PhgrProj/InstrBlock} . Each sub folder
of  {\tt MMVII-PhgrProj/InstrBlock} contains differerent state of computation  of possibly
several bloc, in case there are several block they will be distinguished by their names.

%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{Editing the bloc with  {\tt BlockInstrEdit}}

%-----------------------------------------------------
\subsection{Introduction}

This command can be used for creating and modifying the \emph{structure} of a bloc. The 
command takes a single mandatory parameter which is a folder corresponding to  state of computation,
let {\tt XXX} be this folder.
Let {\tt YYY} be the name of the bloc created, it's default value is
{\tt "TheBlock"} and it can be changed  with optionnal parameter {\tt NameBloc};
as long as we use a single bloc, there is no use to fix the value.
The block will be saved in the file :

\begin{itemize}
    \item  {\tt MMVII-PhgrProj/InstrBlock/XXX/FileRB\_YYY.xml}  ;
\end{itemize}

If the file does not exist, it is created with an empty block. 
If the file exist, it'is possible to reset it to an empty block
with optionnal parameter {\tt FromScratch}.

We call time stamp, an identifier that caracterize the  image (or more
generally any measure) acquired  at the same time : \emph{two images
were acquired simultaneously if and only if they have the same time stamp}.


%-----------------------------------------------------
\subsection{Adding cameras}

The assumption made by \PPP is that two different images , if they
are present in the bloc, occupy the same place inside the bloc \emph{if and only if}
they have they have the same name of intrinsic parameter associated
(because this means that they correspond to the same camera).

The optionnal parameter  for adding camera is {\tt PatsIm4Cam}, it's a
vector containg $1$ to $3$ regular expression, knowing that :

\begin{itemize}
    \item  if not settled the second  equals the first;
    \item  if not settled the third  equals the second;
\end{itemize}


The first pattern indicate a set of image file, for each file the
name of the camera associated to this file is computed, and if not already
present is added to the bloc. Of course, for this to work, this mean 
that user has already given the necessary information for computing the
name of a camera (for example with command {\tt EditCalcMTDI}).

The second pattern indicate how to compute the times stamp from one image.
In this pattern, the first parenthesis expression correpond to the time stamp.
For example :

\begin{itemize}
	\item  Pattern= {\tt [0-9]\{3\}\_([0-9]\{4\}).*.tif} ;
	\item  Image= {\tt 949\_3118-Clino2.tif};
        \item  TimeStamp={\tt 3118}.
\end{itemize}


The third pattern can be used to indicate if an image is included in the bloc.
In fact, it can happen that the same camera  is  used simultaneously
inside and outside a bloc, in this case this pattern can be used to indicate
which images belong to the bloc.

%-----------------------------------------------------
\subsection{Adding clinometers}

The optionnal parameter {\tt InMeasureClino} allow to add 
new clinometers. It's a folder where  the clinometer
measures are stored, generally resulting from the call to command {\tt ImportMeasuresClino}.

It's also possible to add constraint orthogonality between  pairs of clinometers
with parameter {\tt CstrOrthog}, its value :

\begin{itemize}
	\item  is a vector of vector;
	\item  each sub-vector must have a size of $3$ and contain name of clino1, name of clino2,
              and \emph{a priori} sigma of the orthogonality constraint.
\end{itemize}

%-----------------------------------------------------
\subsection{ToDo}

For more complicated case, allow to create the bloc even when there is no data present : 

\begin{itemize}
    \item  explicitely  add cameras by the name of intrinsic calib (w/o images) ;
    \item  explicitely  add clinometers by their name  (w/o measures files).
\end{itemize}

%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{Initializing parameters of the bloc}

%-----------------------------------------------------
\subsection{Introduction}
Like often in photogrammetry, before using parameter in adjustment, we
need approximate values of these parameters for linearizing the equation.
So we need special algorithm, and associated command, for computing the
initial value of these parameters.

%-----------------------------------------------------
%-----------------------------------------------------
%-----------------------------------------------------

\section{Programmer's point of view}




